# Appendix I - Lacerda's Dataset


```{r}
#| label: tbl-lacerda
#| tbl-cap: "Lacerda's dataset"
#| echo: false
#| warning: false
lacerda_example |>
  skimr::skim()
```

# Appendix - Prompt {#sec-annex-prompt}

Lorem ipsum

# Appendix - Fine tune performance {#sec-ft-performance}

Lorem ipsum

# Appendix - Plots and tables {#sec-plots-tables}

Lorem ipsum

# Appendix - Acknowledgments {#sec-thank-you}

Vetor Brasil, ChancenEg. Marina Lacerda Silva, Lynn Kaack, Huy Dang, Sascha. Prof. Susana Henriques da Costa, José Jesus Filho, Associação Brasileira de Jurimetria e Jusbrasil. MDS classes of 2023 and 2025, the Latin-American Club specially the Brazilians. Special thanks to João Vitor Krieger, Renan Barbosa. Also, a grateful to Fernanda Horn, Vitor Moneo, Orisha, Meirelles.

# Appendix - Description of NLP Tasks {#sec-nlp-tasks}

```{r}
#| label: tbl-nlp-task
#| tbl-cap: Mapping of columns to traditional NLP tasks

tibble::tribble(
  ~column,                             ~data_type_task,          ~nlp_task,                    ~explanation,
  # numeric QA
  "maconha_g",                         "numeric",               "numeric_qa",                 "extract numeric value",
  "cocaina_g",                         "numeric",               "numeric_qa",                 "extract numeric value",
  "crack_g",                           "numeric",               "numeric_qa",                 "extract numeric value",
  "ecstasy_g",                         "numeric",               "numeric_qa",                 "extract numeric value",
  "lsd_g",                             "numeric",               "numeric_qa",                 "extract numeric value",
  "tot_pen_meses",                     "numeric",               "numeric_qa",                 "extract numeric value",
  
  # binary classification flags
  "aval_antecedentes",                 "boolean",               "binary_classification",      "binary classification flag",
  "aval_conduta",                      "boolean",               "binary_classification",      "binary classification flag",
  "aval_personalidade",                "boolean",               "binary_classification",      "binary classification flag",
  "aval_natureza",                     "boolean",               "binary_classification",      "binary classification flag",
  "aval_quantidade",                   "boolean",               "binary_classification",      "binary classification flag",
  "aval_variedade",                    "boolean",               "binary_classification",      "binary classification flag",
  "aval_circunstancias",               "boolean",               "binary_classification",      "binary classification flag",
  "aval_consequencias",                "boolean",               "binary_classification",      "binary classification flag",
  "aval_culpabilidade",                "boolean",               "binary_classification",      "binary classification flag",
  "resultado_art_28",                  "boolean",               "binary_classification",      "binary classification flag",
  "resultado_art_33",                  "boolean",               "binary_classification",      "binary classification flag",
  "resultado_art_34",                  "boolean",               "binary_classification",      "binary classification flag",
  "resultado_art_35",                  "boolean",               "binary_classification",      "binary classification flag",
  "denuncia_art_33",                   "boolean",               "binary_classification",      "binary classification flag",
  "denuncia_art_34",                   "boolean",               "binary_classification",      "binary classification flag",
  "denuncia_art_35",                   "boolean",               "binary_classification",      "binary classification flag",
  
  # yes/no QA flags
  "maconha",                           "boolean",               "yesno_qa",                   "yes/no QA flag",
  "maconha_outras",                    "boolean",               "yesno_qa",                   "yes/no QA flag",
  "cocaina",                           "boolean",               "yesno_qa",                   "yes/no QA flag",
  "crack",                             "boolean",               "yesno_qa",                   "yes/no QA flag",
  "ecstasy",                           "boolean",               "yesno_qa",                   "yes/no QA flag",
  "lsd",                               "boolean",               "yesno_qa",                   "yes/no QA flag",
  "outras_drogas",                     "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_local_de_trafico",             "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_preso_no_momento_da_sentenca", "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_confissao_informal",           "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_confissao",                    "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_denuncia_anonima",             "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_denuncia",                     "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_atitude_suspeita",             "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_divergencias_nos_relatos_dos_policiais", "boolean",        "yesno_qa",                   "yes/no QA flag",
  "flag_investigacao",                 "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_interceptacao",                "boolean",               "yesno_qa",                   "yes/no QA flag",
  "flag_mandado",                      "boolean",               "yesno_qa",                   "yes/no QA flag",
  
  # multiclass classification
  "local",                             "categorical",           "multiclass_classification",  "multi-class classification",
  "sentenca",                          "categorical",           "multiclass_classification",  "multi-class classification",
  
  # open-text normalization
  "juiz",                              "open_textual",          "open_text_normalization",    "normalize text field",
  "nome",                              "open_textual",          "open_text_normalization",    "normalize text field",
  
  # span extraction (NER)
  "pena_base",                         "span",                  "named_entity_recognition",   "extract text span",
  "tot_pen",                           "span",                  "named_entity_recognition",   "extract text span"
) |>
  knitr::kable() |>
  kableExtra::kable_paper(
    latex_options = "striped",
    full_width = FALSE,
    font_size = 7
  ) |>
  kableExtra::column_spec(1, width = "15em") |>
  kableExtra::column_spec(2, width = "17em") |>
  kableExtra::column_spec(3, width = "17em") |>
  kableExtra::column_spec(4, width = "20em")

```